Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2022-05-15 paper/ms.tex
Clean up Fig 3

\begin{figure*}[h!]%
\centering
\includegraphics[width=18cm]{fig/fig3.pdf}
\caption{\textbf{The wake excited in the dark matter halo.} The dark matter
halo wake is shown in the \Nbody{} case (\textit{left panel}) and SMUGGLE case
(\textit{right panel}) after $2.6\,\textrm{Gyr}$ of evolution. The
\textit{left} and \textit{right panels} show a surface density projection in
the $x$-$y$ plane of the dark matter halo after an axisymmetric average has
been subracted. The solid line indicates the direction of the bar while the
dashed line indicates the direction of the halo wake (both measured by taking
the second Fourier component within a sphere of all material within a radius
of $4\,\textrm{kpc}$). The \textit{center panel} shows the time evolution of
the angle difference between the bar and the halo wake, as measured from the
second Fourier component. After the first Gyr, the angle difference in the
SMUGGLE case is smaller than in the \Nbody{} case by about a factor of two,
reflecting how the dark matter halo in the SMUGGLE case is unable to exert as
negative a torque on the bar as in the \Nbody{} case.}\label{fig:wake}
\end{figure*}

@@

We can test this interpretation by measuring the angle offset between the halo
wake and the bar. If the wake and the bar are aligned (i.e., there is no angle
offset), then the wake cannot exert a negative torque on the bar. This angle
is plotted in the middle panel of Fig.~\ref{fig:wake}, which shows that the
angle offset is larger in the \Nbody{} case than in the SMUGGLE case by about a
factor of two. The left and right panels of Fig.~\ref{fig:wake} show the halo
wake with respect to the location of the bar in the \Nbody{} (left) and SMUGGLE
(right) cases.

>>>>

\begin{figure*}[h!]%
\centering
\includegraphics[width=18cm]{fig/fig3.pdf}
\caption{\textbf{The wake excited in the dark matter halo.} The dark matter
halo wake is shown in the \Nbody{} case (\textit{middle panel}) and SMUGGLE case
(\textit{right panel}) after $2.6\,\textrm{Gyr}$ of evolution. The
\textit{middle} and \textit{right panels} show a surface density projection in
the $x$-$y$ plane of the dark matter halo after an axisymmetric average has
been subracted. The solid line indicates the direction of the bar while the
dashed line indicates the direction of the halo wake (both measured by taking
the second Fourier component within a sphere of all material within a radius
of $4\,\textrm{kpc}$). The \textit{left panel} shows the time evolution of
the angle difference between the bar and the halo wake, as measured from the
second Fourier component. After the first Gyr, the angle difference in the
SMUGGLE case is smaller than in the \Nbody{} case by about a factor of two,
reflecting how the dark matter halo in the SMUGGLE case is unable to exert as
negative a torque on the bar as in the \Nbody{} case.}\label{fig:wake}
\end{figure*}

@@

We can test this interpretation by measuring the angle offset between the halo
wake and the bar. If the wake and the bar are aligned (i.e., there is no angle
offset), then the wake cannot exert a negative torque on the bar. This angle
is plotted in the left panel of Fig.~\ref{fig:wake}, which shows that the
angle offset is larger in the \Nbody{} case than in the SMUGGLE case by about a
factor of two. The center and right panels of Fig.~\ref{fig:wake} show the halo
wake with respect to the location of the bar in the \Nbody{} (center) and SMUGGLE
(right) cases.
